\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-14 paper/ms.tex
Application references

@@

@@

@@

@@

>>>>

DNS has been applied several times in astrophysics
\citep[e.g.][]{2014MNRAS.445.3055P, 2015ApJ...810...66H, 2015MNRAS.448.3206B}
and was recently used in a biological application \citep{salmonella}.

@@

\bibitem[Brewer and Donovan(2015)]{2015MNRAS.448.3206B} Brewer, B.~J., Donovan, C.~P.\ 2015.\ Fast Bayesian inference for exoplanet discovery in radial velocity data.\ Monthly Notices of the Royal Astronomical Society 448, 3206-3214.

@@

\bibitem[Dybowski et al(2015)]{salmonella}
Dybowski, Richard, et al. Single passage in mouse organs enhances the survival and spread of Salmonella enterica. Journal of The Royal Society Interface 12.113 (2015): 20150702.

@@

\bibitem[Huppenkothen et al.(2015)]{2015ApJ...810...66H} Huppenkothen, D., Brewer, B.~J., Hogg, D.~W., Murray, I., Frean, M., Elenbaas, C., Watts, A.~L., Levin, Y., van der Horst, A.~J., Kouveliotou, C.\ 2015.\ Dissecting Magnetar Variability with Bayesian Hierarchical Models.\ The Astrophysical Journal 810, 66.

@@

\bibitem[Pancoast et al.(2014)]{2014MNRAS.445.3055P} Pancoast, A., Brewer, B.~J., Treu, T.\ 2014.\ Modelling reverberation mapping data - I. Improved geometric and dynamical models and comparison with cross-correlation results.\ Monthly Notices of the Royal Astronomical Society 445, 3055-3072.
